---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE
)

set.seed(0)
```


# wire


<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](https://github.com/YuhangTom/wire/commits/main)
[![Codecov test coverage](https://codecov.io/gh/YuhangTom/wire/branch/main/graph/badge.svg)](https://app.codecov.io/gh/YuhangTom/wire?branch=main)
[![R-CMD-check](https://github.com/YuhangTom/wire/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/YuhangTom/wire/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `wire` is to implement a systematic reproducible automatic algorithm to analyze similarity between wire cut scans.


# Installation


You can install the development version of wire from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("YuhangTom/wire")
```


# Usage


## Data


The original scans for the wire cuts are stored in `x3p` format of width around $2,300$ and height around $1,800$,
under a resolution $0.645 \mu m \times 0.645 \mu m$,
with each file being at least 15 MB,
which is much larger compared to the file limit of 5 MB for a `R` package.
Therefore,
we make available 2 subsampled `x3p` data set by every 10 observations,
saved as entries with its label in a `list` object,
named as `x3p_subsamples`.
The data can be used by:

```{r data}
library(wire)

x3p_subsamples
```


## Inner polygon


To remove edge effect,
we extract the inner part of the scan,
which can be achieved by:

```{r insidepoly}
x3p <- x3p_subsamples[[1]]
insidepoly_df <- x3p_insidepoly_df(x3p, mask_col = "#FF0000", concavity = 1.5, b = 1, ifplot = TRUE)
insidepoly_df %>%
  str()
```


## Remove trend


To remove overall trend on the inner surface,
we can use:

```{r rmtrend}
x3p_inner_nomiss_res <- df_rmtrend_x3p(insidepoly_df)
x3p_inner_nomiss_res
```


## Imputation


We can impute the missing values inside the surface by:

```{r impute}
x3p_inner_impute <- x3p_impute(x3p_inner_nomiss_res, ifsave = FALSE, dir_name = NULL, ifplot = TRUE)
x3p_inner_impute
```


## Rotation


We can rotate the surface to the correct angle by:

```{r rotate}
x3p_bin_rotate <- x3p_vertical(x3p_inner_impute, min_score_cut = 0.1, ifplot = TRUE)
x3p_bin_rotate
```


## Signal extraction


To extract signals from the rotated surface,
two methods are provided,
implemented by
`wire::x3p_raw_sig_vec`
and
`wire::x3p_shift_sig_vec`,
respectively:

```{r signal}
raw_sig <- x3p_raw_sig_vec(x3p_bin_rotate, ifplot = TRUE)
raw_sig %>%
  str()

shift_sig <- x3p_shift_sig_vec(x3p_bin_rotate, ifplot = TRUE)
shift_sig %>%
  str()
```


## Signal alignment


Extracted signals can be aligned and cross correlation can be computed:

```{r align}
vec_align_sigs_list(raw_sig$sig, shift_sig$sig, ifplot = TRUE) %>%
  str()
```

