---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE,
  warning = FALSE
)

set.seed(0)
```


# wire


<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](https://github.com/YuhangTom/wire/commits/main)
[![CRAN
status](https://www.r-pkg.org/badges/version/wire.png)](https://CRAN.R-project.org/package=wire)
[![Codecov test coverage](https://codecov.io/gh/YuhangTom/wire/branch/main/graph/badge.svg)](https://app.codecov.io/gh/YuhangTom/wire?branch=main)
[![R-CMD-check](https://github.com/YuhangTom/wire/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/YuhangTom/wire/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `wire` is to provide a systematic reproducible automatic algorithm to analyze the similarity between wire cut scans.


# Installation


You can install the development version of wire from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("YuhangTom/wire")
```


# Usage


## Data


The original scans for the wire cuts are stored in `x3p` format of width around 2300 and height around 1800,
under a resolution $0.645 \mu m \times 0.645 \mu m$,
with each file being at least 15 MB,
which is much larger compared to the file limit of 5 MB for a `R` package.
Therefore,
we subsampled the original scans by a factor of 10,
and saved them as `x3p_subsamples` in the package.
The data can be used by:

```{r data}
library(wire)

x3p_subsamples
```


## Inner polygon


To remove the edge effect,
we extract the inner part of the scan,
which can be achieved by:

```{r insidepoly}
x3p <- x3p_subsamples[[1]]
insidepoly_df <- x3p_insidepoly_df(x3p, mask_col = "#FF0000", concavity = 1.5, b = 1, ifplot = TRUE)

attr(insidepoly_df, "x3p_plot")
attr(insidepoly_df, "number_of_missing_immediate_neighbors_plot")
attr(insidepoly_df, "standard_deviation_of_non_missing_immediate_neighbors_plot")
attr(insidepoly_df, "number_of_missing_immediate_neighbors_boxplot")
```


## Remove trend


To remove the overall trend on the inner surface,
we can use:

```{r rmtrend}
x3p_inner_nomiss_res <- df_rmtrend_x3p(insidepoly_df)
x3p_inner_nomiss_res
```


## Imputation


We can impute the missing values inside the surface by:

```{r impute}
x3p_inner_impute <- x3p_impute(x3p_inner_nomiss_res, ifout = TRUE, ifsave = FALSE, dir_name = NULL, ifplot = TRUE)
attr(x3p_inner_impute, "x3p_impute_0_plot")
attr(x3p_inner_impute, "x3p_impute_1_plot")
attr(x3p_inner_impute, "x3p_impute_n_plot")
```


## Rotation


We can rotate the surface to the correct angle by:

```{r rotate}
x3p_bin_rotate <- x3p_vertical(x3p_inner_impute, min_score_cut = 5, ifplot = TRUE)

attr(x3p_bin_rotate, "nfline_red_plot")
attr(x3p_bin_rotate, "MLE_loess_red_plot")
attr(x3p_bin_rotate, "nfline_blue_plot")
attr(x3p_bin_rotate, "MLE_loess_blue_plot")
```


## Signal extraction


To extract signals from the rotated surface,
two methods are provided,
implemented by
`wire::x3p_raw_sig_df`
and
`wire::x3p_shift_sig_df`,
respectively:

```{r signal}
raw_sig_df <- x3p_raw_sig_df(x3p_bin_rotate, ifplot = TRUE)
attr(raw_sig_df, "sig_df_plot")

shift_sig_df <- x3p_shift_sig_df(x3p_bin_rotate, ifplot = TRUE)
attr(shift_sig_df, "x3p_before_shift_plot")
attr(shift_sig_df, "x3p_after_shift_plot")
attr(shift_sig_df, "MSE_plot")
attr(shift_sig_df, "sig_df_plot")
```


## Signal alignment


Extracted signals can be aligned,
and the cross-correlation can be computed:

```{r align}
aligned <- vec_align_sigs_list(raw_sig_df$sig, shift_sig_df$sig, ifplot = TRUE)
attr(aligned, "sig_align_plot")
```

